\bf \Large A Model Evaluation Study for Treatment Planning of Laser Induced Thermal Therapy

### 2015-04-27 gpuPlanningAug13.tex
Removed duplicate citation for Curry2012

Approximately 211,000 patients present each year in the US with brain
tumors.  Of these, 38,000 are benign primary tumors, 23,000 malignant
primary tumors, and 150,000 are metastatic, originating largely from lung,
breast, and melanoma~\cite{NCIFact13,
kalkanis2010evidence,gavrilovic2005brain,bafaloukos2004treatment,Owonikoko2014}.
The average life expectancy for patients with primary and metastatic
malignancies in the brain, from time of diagnosis until death, is
approximately 12-16 months. Five year survival is among the lowest of all
cancers. Current treatment options include conventional surgery,
stereotactic radiosurgery (SRS), or chemotherapy.  
Surgical resection may be preferred for patients presenting with a single,
solitary lesion, or lesions greater than 2.5 cm - 3.0 cm in which the size
or location of the tumor causes neurological symptoms such as seizures,
headaches, cognitive or motor deficits, that can be resolved by reducing
the volume of the disease.
SRS, such as Gamma Knife\textsuperscript{\textregistered}, is typically performed on patients with multiple
tumors, tumors under 2.5 cm in diameter, and deep seated tumors~\cite{alexander1995stereotactic}.
An additional target in brain is
epileptogenic foci for patients with medically refractory epilepsy,
where MRgLITT is being considered for the surgical armamentarium for those patients~\cite{curry2012mr,Nowell2014}.
Unfortunately, patients with malignant recurrences who have reached max{\color{red}imum} radiation dose
limitations and complications with surgical resection create a group of
patients with no remaining conventional treatment options;
meanwhile patients with medically refractory epilepsy have limited interventions available.
Magnetic resonance-guided laser induced thermal therapy (MRgLITT) presents
an alternative, minimally invasive thermal ablation technique for these
groups of patients and has been safely and successfully applied to 
each~\cite{carpentieretal08,carpentier2011laser,
carpentier2012mr,torres2013stereotactic,jethwa2012magnetic,
schwarzmaier2002basic,schulze2004laser}.

>>>>

Approximately 211,000 patients present each year in the US with brain
tumors.  Of these, 38,000 are benign primary tumors, 23,000 malignant
primary tumors, and 150,000 are metastatic, originating largely from lung,
breast, and melanoma~\cite{NCIFact13,
kalkanis2010evidence,gavrilovic2005brain,bafaloukos2004treatment,Owonikoko2014}.
The average life expectancy for patients with primary and metastatic
malignancies in the brain, from time of diagnosis until death, is
approximately 12-16 months. Five year survival is among the lowest of all
cancers. Current treatment options include conventional surgery,
stereotactic radiosurgery (SRS), or chemotherapy.  
Surgical resection may be preferred for patients presenting with a single,
solitary lesion, or lesions greater than 2.5 cm - 3.0 cm in which the size
or location of the tumor causes neurological symptoms such as seizures,
headaches, cognitive or motor deficits, that can be resolved by reducing
the volume of the disease.
SRS, such as Gamma Knife\textsuperscript{\textregistered}, is typically performed on patients with multiple
tumors, tumors under 2.5 cm in diameter, and deep seated tumors~\cite{alexander1995stereotactic}.
An additional target in brain is
epileptogenic foci for patients with medically refractory epilepsy,
where MRgLITT is being considered for the surgical armamentarium for those patients~\cite{Curry2012,Nowell2014}.
Unfortunately, patients with malignant recurrences who have reached max{\color{red}imum} radiation dose
limitations and complications with surgical resection create a group of
patients with no remaining conventional treatment options;
meanwhile patients with medically refractory epilepsy have limited interventions available.
Magnetic resonance-guided laser induced thermal therapy (MRgLITT) presents
an alternative, minimally invasive thermal ablation technique for these
groups of patients and has been safely and successfully applied to 
each~\cite{carpentieretal08,carpentier2011laser,
carpentier2012mr,torres2013stereotactic,jethwa2012magnetic,
schwarzmaier2002basic,schulze2004laser}.
